Manuscript draft

### 2019-06-21 manuscript/manuscript draft.Rmd
updated manuscript draft

  ```{r echo=FALSE, out.width='100%', fig.cap = "Graphs of primary productivity $(MgC~ha^-1~yr^-1)$ regressed against latitude. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$. Plots show smaller component fluxes (1) and (2); the larger flux (3) defined by the combination of (1) and (2); and a modelled estimate of the sum of (1) and (2). 95% confidence intervals are plotted for (3)", fig.pos='H'}
  knitr::include_graphics("combined_stacked.png")
  ```

@@

  ```{r echo=FALSE, out.width='100%', fig.cap = "Plots of primary productivity $(MgC~ha^-1~yr^-1)$ regressed against the climate variables identified as the best predictors. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$.", fig.pos='H'}
  knitr::include_graphics("combined_plots.png")
  ```

@@

>>>>

```{r echo=FALSE, out.width='100%', fig.cap = "Graphs of primary productivity $(MgC~ha^-1~yr^-1)$ regressed against latitude. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$. Plots show smaller component fluxes (1) and (2); the larger flux (3) defined by the combination of (1) and (2); and a modelled estimate of the sum of (1) and (2). 95\\% confidence intervals are plotted for (3).", fig.pos='H'}

  knitr::include_graphics("combined_stacked.png")
```

@@

```{r echo=FALSE, out.width='100%', fig.cap = "Plots of primary productivity $(MgC~ha^-1~yr^-1)$ regressed against the climate variables identified as the best predictors: mean annual temperature; temperature seasonality; annual temperature range; and vapour pressure. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$.", fig.pos='H'}
  knitr::include_graphics("combined_plots.png")
```

@@

```{r echo=FALSE, out.width='100%', fig.cap = "Ratio of ANPP foliage to ANPP woody and ANPP woody stem plotted against major ecozones. All pairwise comparisons are significant. Significance levels of pairwise comparisons are indicated where * $p \\leq 0.05 $; ** $p \\leq 0.01 $; *** $p \\leq 0.001 $; **** $p \\leq 0.0001 $.", fig.pos='H'}
  knitr::include_graphics("boxplot_foliage_woody_combined.png")
```
